Internet of Things code deployment metrics

### 2014-11-08 opdracht_2/beamer.tex
skeleton nearly done
Sample application dia

% Created 2014-11-03 Mon 16:56
\documentclass[presentation, bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{hyperref}
\tolerance=1000
\usetheme{kuleuven}
\useinnertheme{rectangles}
\graphicspath{{graphics/}}
\usepackage[style=authoryear,hyperref,backref,square,natbib,ibidtracker=false]{biblatex}
\bibliography{bibliography}
\usepackage[english]{babel}
\usepackage{graphicx}
\usetheme{default}
\author{Ward Schodts, Xavier Goás Aguililla}
\date{maandag 10 november 2014}
\title{Internet of Things code deployment metrics}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.3.1 (Org mode N/A)}}
\begin{document}

@@

\begin{frame}[label=sec-1-2]{Sample applications}
\begin{itemize}
\item military
\item environmental science
\item medicine
\item domotics
\item many more
\end{itemize}
\end{frame}

@@

\begin{frame}[label=sec-3-4]{Plotting voltage}
\includegraphics[width=0.95\textwidth,keepaspectration=true]{energy_measurement_plot}
\end{frame}
\begin{frame}[label=sec-3-5]{Power statistics}
\end{frame}
\begin{frame}[label=sec-3-6]{How to model?}
\begin{itemize}
\item 
\end{itemize}
\end{frame}
\section{Conclusion}
\label{sec-4}
\begin{frame}[label=sec-4-1]{Conclusion}
\end{frame}
\begin{frame}[label=sec-4-2]{Bibliography}
\nocite{*}
\printbibliography
\end{frame}
% Emacs 24.3.1 (Org mode N/A)
\end{document}

>>>>

% Created 2014-11-03 Mon 17:37
\documentclass[presentation, bigger]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amstext}
\usepackage{hyperref}
\tolerance=1000
\usetheme{kuleuven}
\useinnertheme{rectangles}
\graphicspath{{graphics/}}
\usepackage[style=authoryear,hyperref,backref,square,natbib,ibidtracker=false]{biblatex}
\bibliography{bibliography}
\usepackage[english]{babel}
\usepackage{graphicx}
\usetheme{default}
\author{Ward Schodts, Xavier Goás Aguililla}
\date{maandag 10 november 2014}
\title{Internet of Things code deployment metrics}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.3.1 (Org mode N/A)}}
\begin{document}

@@

\begin{frame}[label=sec-1-2]{Sample applications}
%\begin{itemize}
%\item military
%\item environmental science
%\item medicine
%\item domotics
%\item many more
%\end{itemize}

\begin{columns}[t]
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{graphics/sample_applications/fire.jpg}\\
\includegraphics[width=5cm,height=3.5cm]{graphics/sample_applications/military.jpg}
\column{.5\textwidth}
\centering
\includegraphics[width=5cm,height=3.5cm]{graphics/sample_applications/landbouw.jpg}\\
\includegraphics[width=5cm,height=3.5cm]{graphics/sample_applications/medicine.jpg}
\end{columns}
\note{And many more}
\end{frame}

@@

\begin{frame}[label=sec-3-4]{Plotting voltage}
\includegraphics[width=0.95\textwidth,keepaspectration=true]{energy_measurement_plot}
\end{frame}

\begin{frame}[label=sec-3-5]{Power usage}
\begin{itemize}
\item can be derived from voltage measurements
\item can be modeled using linear regression
\end{itemize}
\end{frame}
\section{Conclusion}
\label{sec-4}
\begin{frame}[label=sec-4-1]{Where do we fit in?}
\end{frame}
\begin{frame}[label=sec-4-2]{Conclusion}
\end{frame}
\begin{frame}[label=sec-4-3]{Bibliography}
\nocite{*}
\printbibliography
\end{frame}
% Emacs 24.3.1 (Org mode N/A)
\end{document}
